---
title: "SQL"
output: html_document
---

##Filtering
```{r}
library(sqldf)
library(Lahman)
```

SELECT and FROM and where

Example 1:

Homerun Totals of the 1927 Yankees

```{r}
query<-"Select HR, playerID,teamID From Batting
where teamID='NYA'and yearID=1927"
sqldf(query)
```


Yankees Hitting 40 or More Homeruns

```{r}
query<-"Select HR, playerID, yearID, teamID FROM Batting
where HR>=40 and teamID='NYA'"
sqldf(query)
```

Example 3 Any Player More than 40 Homeruns but less than 60 Strikeouts

```{r}
query<-"Select HR, playerID, teamID, SO From Batting
where HR>40 and SO<60"
sqldf(query)
```

Example 4 - 1970's Phillies Hitting More than 30 Homeruns

```{r}
query<-"Select HR, playerID, yearID, teamID From Batting
where HR>30 and teamID='PHI' and yearID>1969 and yearID<1980"
sqldf(query)
```
##Ordering

Example 1 - Every time a player hit 50 or more Homeruns from highest to lowest total

```{r}
query<-"select HR, playerID, teamID from Batting
where HR>=50 
Order By HR DESC"
sqldf(query)


```
Example 2 - Find all instances of a player striking out less than 10 times. Make sure each player has at least 400 at bats. Order by least to most strikeouts
```{r}
query<-"select SO, AB, playerID, teamID, yearID from Batting where SO<10 and AB>=400 Order by SO"
sqldf(query)
```

find the career home run total for babe ruth

```{r}
query<-"select sum(HR), playerID from Batting where playerID='ruthba01' group by playerID"
sqldf(query)
```

find the career hR totals of any player who had 600 or more career hR, desc order
```{r}
query<-"select sum(HR), playerID from Batting group by playerID having sum(HR)>=600 order by sum(HR) Desc"
sqldf(query)
```
Players who have the highest average per season HR, avg over 30, desc

```{r}
query<-"select avg(HR), playerID from Batting group by playerID having avg(HR)>30 order by avg(HR) desc"
sqldf(query)
```

First and last name along with the team, year, HR Babe ruth
```{r}
query<-"select nameFIRST,nameLAST, teamID, yearID, HR from Batting 
inner join Master ON Batting.playerID=Master.playerID where Batting.playerID='ruthba01'"
sqldf(query)
```

