---
title: "SQL"
output: html_document
---

##Filtering
```{r}
library(sqldf)
library(Lahman)
```

SELECT and FROM and where

Example 1:

Homerun Totals of the 1927 Yankees

```{r}
query<-"Select HR, playerID,teamID From Batting
where teamID='NYA'and yearID=1927"
sqldf(query)
```


Yankees Hitting 40 or More Homeruns

```{r}
query<-"Select HR, playerID, yearID, teamID FROM Batting
where HR>=40 and teamID='NYA'"
sqldf(query)
```

Example 3 Any Player More than 40 Homeruns but less than 60 Strikeouts

```{r}
query<-"Select HR, playerID, teamID, SO From Batting
where HR>40 and SO<60"
sqldf(query)
```

Example 4 - 1970's Phillies Hitting More than 30 Homeruns

```{r}
query<-"Select HR, playerID, yearID, teamID From Batting
where HR>30 and teamID='PHI' and yearID>1969 and yearID<1980"
sqldf(query)
```
##Ordering

Example 1 - Every time a player hit 50 or more Homeruns from highest to lowest total

```{r}
query<-"select HR, playerID, teamID from Batting
where HR>=50 
Order By HR DESC"
sqldf(query)


```
Example 2 - Find all instances of a player striking out less than 10 times. Make sure each player has at least 400 at bats. Order by least to most strikeouts
```{r}
query<-"select SO, AB, playerID, teamID, yearID from Batting where SO<10 and AB>=400 Order by SO"
sqldf(query)
```

find the career home run total for babe ruth

```{r}
query<-"select sum(HR), playerID from Batting where playerID='ruthba01' group by playerID"
sqldf(query)
```

find the career hR totals of any player who had 600 or more career hR, desc order
```{r}
query<-"select sum(HR), playerID from Batting group by playerID having sum(HR)>=600 order by sum(HR) Desc"
sqldf(query)
```
Players who have the highest average per season HR, avg over 30, desc

```{r}
query<-"select avg(HR), playerID from Batting group by playerID having avg(HR)>30 order by avg(HR) desc"
sqldf(query)
```

##Joining
First and last name along with the team, year, HR Babe ruth
```{r}
query<-"select nameFIRST,nameLAST, teamID, yearID, HR from Batting 
inner join Master ON Batting.playerID=Master.playerID where Batting.playerID='ruthba01'"
sqldf(query)
```
Question 2: Find all instances of players getting more than 50 homeruns starting with the greatest number. Include first and last names, team, year, and home runs.
```{r}
query<-"SELECT nameFIRST,nameLAST,teamID,yearID,HR
FROM Batting INNER JOIN Master
On Batting.playerID=Master.playerID WHERE HR>50 ORDER BY HR DESC"
sqldf(query)
```

Question 3:Find Babe Ruth's homeruns by season, with the team name displayed.

```{r}
query<-"SELECT playerID,name,Batting.yearID,Batting.HR
FROM Batting INNER JOIN Teams
ON Batting.teamID=Teams.teamID and Batting.yearID=Teams.yearID
WHERE playerID='ruthba01'"
sqldf(query)

```

Question 4: Find Babe Ruth's homerun totals, with first and last name and the full team name displayed.

```{r}
query<-"SELECT nameFIRST,nameLAST,name,Batting.yearID,Batting.HR 
FROM (Batting INNER JOIN Master
ON Batting.playerID=Master.playerID) INNER JOIN Teams 
ON Batting.teamID=Teams.teamID and Batting.yearID=Teams.yearID
WHERE Batting.playerID='ruthba01'"
sqldf(query)

```
Question 5: Find career homerun totals for players who have at least 600 homeruns. Display from the highest amount to the lowest, with the first and last names.
```{r}
query<-"SELECT nameFIRST,nameLAST,sum(HR)
FROM Batting INNER JOIN Master
ON Batting.playerID=Master.playerID
GROUP BY Batting.playerID
HAVING sum(HR)>=600
ORDER BY sum(HR) DESC"
sqldf(query)
```

Question 6: List all players, first and last name, with the first name of Bob who averaged more than one million dollars salary over their career.

```{r}
query<-"SELECT nameFIRST,nameLAST,avg(salary)
FROM Salaries INNER JOIN Master
ON Salaries.playerID=Master.playerID
GROUP BY Salaries.playerID
HAVING nameFIRST='Bob' and avg(salary)>1000000
ORDER BY avg(salary) DESC"
sqldf(query)
```


